\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulation performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.\blue{XX}), respectively, which are close match to the expected from equation

%and viscosity ratios 10$^{2}\le${\it VR}$\le$10$^{4}$ and 632$\leN_{C}^{'}\le$6.32$\times$10$^{7}$. 
%the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate

>>>>

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively. This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).
